Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-05-02 paper-correlations.tex
A note about preprocessing
Add units of measurement

\section{The scan approach.}
\label{sec:scan}
All algorithms described above are executed on the whole input and hence require
a lot of memory. The scan approach deals with memory limitations at the cost of
higher execution time. In this approach we select a list of predefined
directions and cut all one-dimensional slices from the input along those
directions. Then for each direction we use an appropriate algorithm in
\cref{sec:map} to calculate a correlation function just for that slice. When all
slices are processed we calculate the result using the formula:
\begin{equation*}
  F^{\bm{d}}(r) = \frac{\sum\limits_i F^{\bm{d}}_i(r) N_i(r)}{\sum\limits_i N_i(r)}
\end{equation*}
Here $F^{\bm{d}}(r)$ is a correlation function computed with respect to a
direction $\bm{d}$, $F^{\bm{d}}_i(r)$ is a ``partial'' correlation
function calculated for a $i$-th slice and $N_i(r)$ is a total number of trials
for a correlation length $r$ and slice $i$.

@@

To test out package we generate a realization of random overlapping disks
(\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
parameters $R = 40$ and $\lambda = 10^{-4}$ and compare calculated correlation
functions with their theoretical values. The results are present on
\cref{fig:verification}.
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\linewidth]{images/disks-fragment.png}
  \caption[]{A fragment of overlapping disks used in testing of our library.}
  \label{fig:overlapping-disks}
\end{figure}

@@

To test out package we generate a realization of random overlapping disks
(\cref{fig:overlapping-disks}) with dimensions $500 \times 500 \times 500$ and
parameters $R = 10$ and $\lambda = 10^{-4}$ and compare calculated correlation
functions with their theoretical values. The results are present on
\cref{fig:verification}.

>>>>

\section{The scan approach.}
\label{sec:scan}
All algorithms described above are executed on the whole input and hence require
a lot of memory. The scan approach deals with memory limitations at the cost of
higher execution time. In this approach we select a list of predefined
directions and cut all one-dimensional slices from the input along those
directions. Then for each direction we use an appropriate algorithm in
\cref{sec:map} to calculate a correlation function just for that slice. When all
slices are processed we calculate the result using the formula:
\begin{equation*}
  F^{\bm{d}}(r) = \frac{\sum\limits_i F^{\bm{d}}_i(r) N_i(r)}{\sum\limits_i N_i(r)}
\end{equation*}
Here $F^{\bm{d}}(r)$ is a correlation function computed with respect to a
direction $\bm{d}$, $F^{\bm{d}}_i(r)$ is a ``partial'' correlation
function calculated for a $i$-th slice and $N_i(r)$ is a total number of trials
for a correlation length $r$ and slice $i$. Some algorithms require
preprocessing stages before cutting the input in slices, e.g. image filtering
for edge detection or connected components labeling is performed on the whole
array, not on slices.

@@

To test out package we generate a realization of random overlapping disks
(\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
parameters $R = 40\ px$ and $\lambda = 10^{-4}\ px^{-2}$ and compare calculated
correlation functions with their theoretical values. The results are present on
\cref{fig:verification}.
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\linewidth]{images/disks-fragment.png}
  \caption[]{A fragment of overlapping disks used in testing of our library.}
  \label{fig:overlapping-disks}
\end{figure}

@@

To test out package we generate a realization of random overlapping disks
(\cref{fig:overlapping-disks}) with dimensions $500 \times 500 \times 500$ and
parameters $R = 10\ px$ and $\lambda = 10^{-4}\ px^{-3}$ and compare calculated
correlation functions with their theoretical values. The results are present on
\cref{fig:verification}.
